---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Graphs

<!-- badges: start -->
<!-- badges: end -->

This site is the home, a personal package, and a vehicle for graphs made with R. It installs the source code of illustrations and other graphs that I made and provides convenient functions to make graphs with `ggplot2` (e.g. slope plots.)

## Installation

You can install Graphs from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("edgar-treischl/Graphs")
```

## Example

Without input, the `plotgraph()` function returns all available graphs.

```{r example, warning=TRUE, error=TRUE}
library(Graphs)
plotgraph()
```

The `plotgraph()` function just picks the installed source code and returns the graphs. For example, the `datasaurus` plot.

```{r, warning=FALSE, message=FALSE}
## basic example code
plotgraph("datasaurus.R")
```

And the package gives access to convenient functions to make `ggplot2` graphs with less effort. For example, `ggslope()` returns a slope chart.

```{r}
library(tidyr)
library(ggplot2)
df <- tribble(
 ~times, ~country,  ~gdp, ~inc,
 "1990",   "A",  22.3, TRUE,
 "2000",   "A",  44.6, TRUE,
 "1990",   "B",  12.3, FALSE,
 "2000",   "B",  4.6, FALSE
 )

ggslope(df,
         times = times,
         outcome = gdp,
         group = country)+
  theme_minimal()
```


